Community-Conditioned Language Models

### 2020-11-11 paper/paper.tex
update in light of new results

- Correlation with co-occurence matrix (not conclusive)

- Analysis: probably because the model is not using dimensions
with \emph{a priori} equal variance in all dimensions. (Both the LSTM and transformer are highly non-linear complex models)

\subsection{Implicit language-model-based community classifiers}

(TODO: Insert a the correlation plot between two models, on the exponential scale so that it's the same as the other later plots)
TODO: So we can't use the losses directly. Why is this so?

@@

TODO: show a few relevant matrices. (eg. show only best and worst model) and commentary.

@@

@@

TODO: show a scatter plot, compute r2, analyse out-of-balance points; discuss why they stand where they do.

Finally, we investigate the correlation between the stability of a
community and the perplexity of the LMCC for it. Stability is defined as TODO.

- compute pearson correlation coefficient

We see a positive correlation: this suggests that the more stable a
community is, the more difficult it is to identify comment as coming
from it. What this suggests is that stable communities tend to use a
varied and standard, subset of English, while unstable communities
resort to more formulaic language. This may suggests that to 'fit' in an
unstable community, one must use more obvious linguistic cues than in
a stable community. In fact, it is reasonable to think that a new
member will ostensibly use community-specifc language, but once
established in a community, a member would tend not to do so.

>>>>

As a quantitative ....

- Correlation with community embeddings based on co-occurence;

- Description of the snap data (JP)

- Insert scatterplot (select 1 model)
  + pearson r for ``all'' models.

\subsection{Latent language-model-based community classifiers}

- Two different use of the model
1. ``absolute'' perplexity
2. latent ability to recognize a community

@@

@@

TODO: scatterplot/r2 between LMCC and CCLM perplexity  ---> no correlation.

@@

TODO: show a scatter plot, compute r2 --> almost perfect correlation

% Finally, we investigate the correlation between the stability of a
% community and the perplexity of the LMCC for it. Stability is defined as TODO.

% - compute pearson correlation coefficient

% We see a positive correlation: this suggests that the more stable a
% community is, the more difficult it is to identify comment as coming
% from it. What this suggests is that stable communities tend to use a
% varied and standard, subset of English, while unstable communities
% resort to more formulaic language. This may suggests that to 'fit' in an
% unstable community, one must use more obvious linguistic cues than in
% a stable community. In fact, it is reasonable to think that a new
% member will ostensibly use community-specifc language, but once
% established in a community, a member would tend not to do so.
